### 2022-04-06 chapters/intro/intro.tex
version impression

\begin{figure}
    \centering
    \includegraphics[width=.8\textwidth]{chapters/intro/figures/anthropocene.png}
    \caption{Goods and services of coral reefs and their linkage with human activities. \modif{Despite covering less than 0.5\% of the ocean floor, coral reefs are home for almost of third of the marine biodiversity and are a source of food and livelihood to hundreds of millions of people.} Source: \cite{hughes2017coral}}
    \label{intro:corals}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.8\textwidth]{chapters/intro/figures/anthropocene.png}
    \caption{Goods and services of coral reefs and their linkage with human activities. \modif{Despite covering less than 0.5\% of the ocean floor, coral reefs are home for almost a third of the marine biodiversity and are a source of food and livelihood to hundreds of millions of people.} Source: \cite{hughes2017coral}}
    \label{intro:corals}
\end{figure}
